```{r echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width=8,
  fig.height=6,
  fig.path="figs/",
  echo = TRUE
)

```

[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/reconhub)](https://cran.r-project.org/package=reconhub)

# *reconhub*

This packages installs and loads all stable RECON packages similiar to the [tidyverse](https://github.com/tidyverse/tidyverse) package.

Work in progress.

## Installing the package

To install the current stable, CRAN version of the package, type:
```{r install, eval = FALSE}
install.packages("reconhub")
```

To benefit from the latest features and bug fixes, install the development, *github* version of the package using:
```{r install2, eval = FALSE}
devtools::install_github("reconhub/reconhub")
```

Note that this requires the package *devtools* installed.


# What does it do?

```{r, eval = FALSE}
# attaches all stable recon packages
library(reconhub)
```



## Getting help online

Bug reports and feature requests should be posted on *github* using the [*issue*](http://github.com/reconhub/epicontacts/issues) system. All other questions should be posted on the **RECON forum**: <br>
[http://www.repidemicsconsortium.org/forum/](http://www.repidemicsconsortium.org/forum/)

Contributions are welcome via **pull requests**.

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.

