---
output: github_document
---
[![Build Status](https://travis-ci.org/reconhub/reconhub.svg?branch=master)](https://travis-ci.org/reconhub/reconhub)
[![Build status](https://ci.appveyor.com/api/projects/status/neg802qc3673exun?svg=true)](https://ci.appveyor.com/project/dirkschumacher/reconhub)
[![Coverage Status](https://img.shields.io/codecov/c/github/reconhub/reconhub/master.svg)](https://codecov.io/github/reconhub/reconhub?branch=master)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/reconhub)](https://cran.r-project.org/package=reconhub)

# *reconhub*

This packages installs and loads all stable RECON packages similiar to the [tidyverse](https://github.com/tidyverse/tidyverse) package.

## Installing the package

To install the current stable, CRAN version of the package, type:
```{r install, eval = FALSE}
install.packages("reconhub")
```

To benefit from the latest features and bug fixes, install the development, *github* version of the package using:
```{r install2, eval = FALSE}
devtools::install_github("reconhub/reconhub")
```

Note that this requires the package *devtools* installed.


# What does it do?

```{r, eval = TRUE}
# attaches all stable recon packages
library(reconhub)
```

Also, you can install all development versions of RECON packages:

```{r, eval = FALSE}
reconhub::install_dev_versions()
```


## Getting help online

Bug reports and feature requests should be posted on *github* using the [*issue*](http://github.com/reconhub/reconhub/issues) system. All other questions should be posted on the **RECON forum**: <br>
[http://www.repidemicsconsortium.org/forum/](http://www.repidemicsconsortium.org/forum/)

Contributions are welcome via **pull requests**.

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.

